---
title: "linear model"
author: "Xiaoyu Wu"
date: "2023-11-28"
output: github_document
---

```{r setup}
library(readxl)
library(dplyr)
library(ggplot2)
library(plotly)
library(modelr)
library(purrr)
library(tidyr)
```

## Import the Data 
```{r}
file_path = "./PL_1819_data.xlsx"


player_df = read_excel(file_path, sheet = 4)
```

## Data Wrangling 
```{r}
cleaned_player_df = player_df  |> 
 mutate(Age = as.numeric(as.character(Age)),
 Min = as.numeric(as.character(Min)))  |> 
 na.omit()
```



## Perform Correlation Analysis 
```{r}
correlation_result = cor.test(cleaned_player_df$Age, cleaned_player_df$Min)

# Printing the results
print(correlation_result)
```

#### Discussion 
The Pearson correlation coefficient between Age (independent variable) and Minutes Played (dependent variable) is approximately 0.137, with a p-value of about 0.0019.

This correlation coefficient suggests a slight positive association between Age and Minutes Played, meaning that as Age increases, there is a slight tendency for Minutes Played to also increase. However, the correlation is relatively weak.

The p-value indicates that this association is statistically significant, assuming a conventional significance level (e.g., 0.05). This means that the observed association is unlikely to be due to random chance. 

## Try to Transform Min into log(Min) for fitting linear model 
```{r}
cleaned_player_df$logMin = log(cleaned_player_df$Min)

model = lm(logMin ~ Age, data = cleaned_player_df)

summary(model)

# Optional: To visualize the model, you can create a scatterplot with the regression line
ggplot(cleaned_player_df, aes(x = Age, y = logMin)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle("Scatterplot of Age vs log(Min) with Linear Model") +
  xlab("Age") +
  ylab("log(Minutes Played)") +
  theme_minimal()
```

## Cross Validation
```{r}
cv_df = 
  crossv_mc(cleaned_player_df, 100)

cv_df =
  cv_df |> 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df = 
  cv_df |> 
  mutate(
    model  = map(train, \(cleaned_player_df) lm(logMin ~ Age, data = cleaned_player_df))
    ) |> 
  mutate(
    rmse_model = map2_dbl(model, test, \(model, cleaned_player_df) rmse(model = model, data = cleaned_player_df)))

cv_df |> 
  select(starts_with("rmse")) |> 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") |> 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

